---
title: "Sol's pecification"
author: "Rebecca"
date: "5/9/2018"
output: html_document:
    keep_md: true
---

```{r setup, include=FALSE}
#install.packages('lubridate')
#install.packages('stringr')
# install.packages("ggthemes")
# install.packages("pander")
# install.packages('ggeffects')
library(lubridate)
library(sparklyr)
library(dplyr)
library(ggplot2)
library(scales)
library(jsonlite)
library(stringr)
library(fuzzyjoin)
library(tidyr)
library(magrittr)
library(ggthemes)
library(knitr)
library(sjPlot)
library(pander)
library(ggeffects)
library(lme4)

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  cache.path = '/home/hadoop/analyses/rweiss/pioneer-news-analysis/cache/',
  cache.extra = list(R.version, sessionInfo(), format(Sys.Date(), '%Y-%m')),
  fig.path = "fig/")
  

#spark config
Sys.setenv(SPARK_HOME='/usr/lib/spark')
config <- spark_config()
config$spark.driver.memory <- "5G"
config$spark.executor.memory <- "10G"
#config$spark.yarn.executor.memoryOverhead <- "1G"
config$spark.executor.cores <- 15
config$spark.executor.instances <- 10
config$spark.sql.shuffle.partitions <- 320
sc <- spark_connect(master = "yarn-client", version = "1.6.2", config = config)

#dwell_parquet_dir = 's3://net-mozaws-data-us-west-2-data-pioneer-analysis/online_news_v2/dwell_time_complete/'
dwell_parquet_dir = 's3://net-mozaws-data-us-west-2-data-pioneer-analysis/online_news_v2/dwell_time_new_handling/'
dwell_tbl = spark_read_parquet(sc, name='dwell_tbl', path=dwell_parquet_dir, repartition=500, memory=F) %>% 
  select(-document_ids, -log_events, -nav_event_count)

activity_tbl = dwell_tbl %>% 
  filter(domain != 'youtube.com' & domain != 'google.com' & domain!= 'facebook.com' & domain != 'youtube.com') %>% 
  filter(visit_start_date > "2018-01-01" & visit_start_date <"2018-05-01") %>% # remove odd clients, likely clock skew
  filter(days_since_appearance > 0 & days_since_appearance < 22) %>% # only look at study periods
  ft_string_indexer(input_col='pioneer_id', output_col='id') %>% # recode pioneer ids
  mutate(
    stage = case_when(
      days_since_appearance == 0 ~ 'enrollment',
      days_since_appearance > 0 & days_since_appearance < 7 ~ 'pretreatment',
      days_since_appearance >= 7 & days_since_appearance < 14 ~ 'treatment',
      days_since_appearance >=14 & days_since_appearance < 21 ~ 'posttreatment',
      days_since_appearance >=22 ~ 'after'),
    total_active_time = total_dwell_time - total_idle_time) %>%
  filter(total_active_time < 5000) %>% # remove clients with active time greater than 99.999%
  compute('activity_tbl')

source('/home/hadoop/analyses/rweiss/pioneer-news-analysis/survey_recoding.R')

bias_json = 'https://raw.githubusercontent.com/mozilla/pioneer-study-online-news-2/master/extension/bias-domains.json'
whois_json = 'https://raw.githubusercontent.com/mozilla/pioneer-study-online-news-2/master/extension/whois-domains.json'
bias_scores = fromJSON(bias_json)
whois_scores = fromJSON(whois_json)
bias_scores$domain = str_replace(bias_scores$domain, 'www.','')

domains = dwell_tbl %>% group_by(domain) %>% count %>% collect
scored_domains = inner_join(bias_scores, domains, by='domain')
names(scored_domains) = c('domain', 'score','n')
scored_domains_tbl = sdf_copy_to(sc,scored_domains, overwrite = T)

pid_tbl = sdf_copy_to(sc,pid, overwrite=T)
valids_tbl = sdf_copy_to(sc,valids,overwrite=T)

scored_browsing_tbl = activity_tbl %>%
  inner_join(scored_domains_tbl) %>%
  group_by(id, stage, days_since_appearance, branch, domain, score) %>%
  summarise(
    mean_active_time_s = mean(total_active_time, na.rm=T),
    total_active_time_s = sum(total_active_time, na.rm=T)) %>%
  compute('scored_browsing_tbl') 

head(scored_browsing_tbl)

```

# Data prep

```{r}
scored_browsing_tbl %>% 
  sdf_pivot(id + days_since_appearance + branch + domain + score + mean_active_time_s + total_active_time_s ~ stage) %>% # creates columns for stage dummy
  na.replace(0) %>% # replaces NaNs with 0s in the stage dummy matrix
  filter(id==1098 & domain=='aol.com')

```
# Specification 1

```{r}
scored_browsing_tbl %>% 
  filter(stage != 'treatment') %>%
  group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
  mutate(
    scored_active_time_s = mean_active_time_s * abs(score)
  ) %>%
  filter(id==1098 & domain=='aol.com')

```

```{r}
tmp = scored_browsing_tbl %>% 
  filter(stage != 'treatment') %>%
  group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
  mutate(
    scored_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
  ) %>%
  ungroup %>% group_by(id, days_since_appearance, total_active_time_s) %>%
  mutate(
    total_perday_active_time_s = sum(total_active_time_s, na.rm=T) # computes total active time on scored domains for the day
  ) 

tmp
sdf_quantile(tmp, column='scored_active_time_s', probabilities=c(0,.25,.5,.75,.9,.99,.999,1))
sdf_quantile(tmp, column='total_perday_active_time_s', probabilities=c(0,.25,.5,.75,.9,.99,.999,1))

```

```{r}
# scored_browsing_tbl %>% 
#   filter(stage != 'treatment') %>%
#   group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
#   mutate(
#     scored_perday_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
#   ) %>%
#   ungroup %>% group_by(id, days_since_appearance, total_active_time_s) %>%
#   mutate(
#     total_perday_active_time_s = sum(total_active_time_s, na.rm=T) # computes total active time on scored domains for the day
#   ) %>%
#   sdf_pivot(id + days_since_appearance + domain + branch + scored_perday_active_time_s + total_perday_active_time_s ~ stage) %>%
#   mutate(
#     scaled_scored_active_time_s = scored_perday_active_time_s/total_perday_active_time_s
#   ) %>% select(-scored_perday_active_time_s, -total_perday_active_time_s) %>%
#   filter(id==1098 & domain=='aol.com')
```
```{r}
# options(scipen=10000)
# scored_browsing_tbl %>%
#   filter(stage != 'treatment') %>%
#   group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
#   mutate(
#     scored_perday_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
#   ) %>%
#   ungroup %>% group_by(id, days_since_appearance, total_active_time_s) %>%
#   mutate(
#     total_perday_active_time_s = sum(total_active_time_s, na.rm=T) # computes total active time on scored domains for the day
#   ) %>%
#   sdf_pivot(id + days_since_appearance + domain + branch + scored_perday_active_time_s + total_perday_active_time_s ~ stage) %>%
#   mutate(
#     scaled_scored_active_time_s = scored_perday_active_time_s/total_perday_active_time_s
#   ) %>% select(-scored_perday_active_time_s, -total_perday_active_time_s) %>%
#   sdf_quantile(column='scaled_scored_active_time_s', probabilities=c(0,.25,.5,.75,.9,.99,.999,1))
```

```{r}



```

```{r}
scored_browsing_tbl %>% 
  filter(stage != 'treatment') %>%
  group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
  mutate(
    scored_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
  ) %>%
  filter(id==1098 & domain=='aol.com') %>% ungroup %>%
  select(-total_active_time_s, -mean_active_time_s, -score)
```

```{r}
scored_browsing_tbl %>% 
  filter(stage != 'treatment') %>%
  group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
  mutate(
    scored_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
  ) %>%
  ungroup %>% select(-mean_active_time_s, -score) %>%
  group_by(id, stage, branch) %>%
  mutate(
    avg_scored_active_time_s = mean(scored_active_time_s, na.rm=T)
  ) %>% 
  ungroup %>% select(-scored_active_time_s, -total_active_time_s, -domain) %>%
  sdf_pivot(id + branch + avg_scored_active_time_s ~ stage) %>%
  mutate(
     posttreatment = (posttreatment/posttreatment)*avg_scored_active_time_s, # fill treatment dummy with mean value
     pretreatment = (pretreatment/pretreatment)*avg_scored_active_time_s # fill treatment dummy with mean value
   ) %>% 
  ungroup %>% select(-avg_scored_active_time_s) %>% group_by(id, branch) %>%
  mutate(
   posttreatment = sum(posttreatment, na.rm=T),
   pretreatment = sum(pretreatment, na.rm=T)
  )
```
```{r}
spec1a_tbl = scored_browsing_tbl %>% 
  filter(stage != 'treatment') %>%
  group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
  mutate(
    scored_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
  ) %>%
  ungroup %>%
  select(-mean_active_time_s, -score) %>%
  group_by(id, stage, branch) %>%
  mutate(
    avg_scored_active_time_s = mean(scored_active_time_s, na.rm=T)
  ) %>% 
  ungroup %>% select(-scored_active_time_s, -total_active_time_s, -domain) %>%
  sdf_pivot(id + branch + avg_scored_active_time_s ~ stage) %>%
  mutate(
     posttreatment = (posttreatment/posttreatment)*avg_scored_active_time_s, # fill treatment dummy with mean value
     pretreatment = (pretreatment/pretreatment)*avg_scored_active_time_s # fill treatment dummy with mean value
   ) %>% 
  ungroup %>% group_by(id, branch) %>%
  mutate(
   posttreatment = sum(posttreatment, na.rm=T),
   pretreatment = sum(pretreatment, na.rm=T)
  ) %>%
  collect %>%
  distinct(id, .keep_all=T)
```

Posttreatment - mean( post-treatment average time on site x bias of site )
Pretreatment - mean( pre-treatment average time on site x bias of site )
Branch - bias, whois, control

Unit of analysis is single user
```{r}
paste('Number of missing posttreatments =', sum(is.na(spec1a_tbl$posttreatment)))
paste('Number of missing pretreatments =', sum(is.na(spec1a_tbl$pretreatment)))
paste('Number of rows =', dim(spec1a_tbl)[1])

fit1a = glm(posttreatment ~ pretreatment*branch + branch, data=spec1a_tbl)
sjt.glm(fit1a)
plot_model(fit1a, rm.terms = 'pretreatment')
```



# Specification 2

Average time on site (post) ~ Average time on site (pre) + alignment (bias) * branch + (1|site)

```{r}
spec2a_tbl = scored_browsing_tbl %>% 
  filter(stage != 'treatment') %>%
  sdf_pivot(id + days_since_appearance + domain + score + branch + mean_active_time_s ~ stage) %>%
  mutate(
    posttreatment = posttreatment*mean_active_time_s, # fill treatment dummy with mean value
    pretreatment = pretreatment*mean_active_time_s # fill treatment dummy with mean value
  ) %>%
  group_by(id, domain) %>%
  select(-mean_active_time_s) %>%
  mutate(
   posttreatment = log(sum(posttreatment, na.rm=T)),
   pretreatment = log(sum(pretreatment, na.rm=T))
  ) %>%
  na.replace(0) %>%
  #filter(row_number(id) == 1) %>% ungroup %>%
  collect

spec2b_tbl = scored_browsing_tbl %>% 
  filter(stage != 'treatment') %>%
  sdf_pivot(id + domain + score + branch + mean_active_time_s ~ stage) %>% # creates columns for stage dummy
  mutate(
    posttreatment = posttreatment*mean_active_time_s,
    pretreatment = pretreatment*mean_active_time_s
  ) %>%
  group_by(id, domain) %>%
  select(-mean_active_time_s) %>%
  mutate(
   posttreatment = log(sum(posttreatment, na.rm=T)),
   pretreatment = log(sum(pretreatment, na.rm=T))
  ) %>%
  filter(row_number(id) == 1) %>% ungroup() %>%
  na.replace(0) %>%
  collect

spec2c_tbl = scored_browsing_tbl %>%
  filter(stage != 'treatment') %>%
  group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
  mutate(
    scored_avg_perday_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
  ) %>%
  ungroup %>%
  sdf_pivot(id + days_since_appearance + domain + branch + score + scored_avg_perday_active_time_s ~ stage) %>%
  mutate(
    posttreatment = log(posttreatment*scored_avg_perday_active_time_s), # fill treatment dummy with mean value
    pretreatment = log(pretreatment*scored_avg_perday_active_time_s) # fill treatment dummy with mean value
  ) %>%
  ungroup %>% select(-scored_avg_perday_active_time_s) %>%
  group_by(id, domain, score, days_since_appearance) %>%
  arrange(id, days_since_appearance) %>%
  na.replace(0) %>%
  collect
```
```{r}
spec2a_tbl %>% filter(id==1098)
spec2b_tbl %>% filter(id==1098)
spec2c_tbl %>% filter(id==1098)
```

```{r}

spec2a_tbl$branch = factor(spec2a_tbl$branch)
fit2a = lmer(posttreatment ~ pretreatment + abs(score) * branch + (1|id), data=spec2a_tbl)
sjt.lmer(fit2a)
plot_model(fit2a, rm.terms = 'pretreatment')

spec2b_tbl$branch = factor(spec2b_tbl$branch)
fit2b = lmer(posttreatment ~ pretreatment + abs(score) * branch + (1|id), data=spec2b_tbl)
sjt.lmer(fit2b)
plot_model(fit2b, rm.terms = 'pretreatment')

spec2c_tbl$branch = factor(spec2c_tbl$branch)
fit2c = lmer(posttreatment ~ pretreatment + abs(score) * branch + (1|id), data=spec2c_tbl)
sjt.lmer(fit2c)
plot_model(fit2c, rm.terms = c('pretreatment', 'abs(score)'))
```

# Specification 3 

Has average score changed over time?

```{r}

```

