---
title: "Other specifications"
author: "Rebecca"
date: "5/9/2018"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  cache.path = '/home/hadoop/analyses/rweiss/pioneer-news-analysis/cache/',
  cache.extra = list(R.version, sessionInfo(), format(Sys.Date(), '%Y-%m')),
  fig.path = "fig/")

source('/home/hadoop/analyses/rweiss/pioneer-news-analysis/make_browsing_tables.R')
source('/home/hadoop/analyses/rweiss/pioneer-news-analysis/recode_survey.R')

```

# Data prep

* Data constructed from raw dwell event log data
* Each row is an individual user initiating a dwell event on a specific URL (truncated to tld+1)

## Schema
--
--
--
--

```{r}
head(dwell_tbl)
```

* Remove google.com, youtube.com, facebook.com, youtube.com, amazon.com
* Remove invalid timestamps
* Remove days outside of study periods
* Construct variable for indicating stage
* Compute "active" time as dwell time less idle time on each dwell event

```{r}
head(activity_tbl)
```

* Remove all browsing not matched to the alignment scores
* Compute mean active time per domain on a day in the study
* Compute total active time per domain on a day in the study
```{r}
head(scored_browsing_tbl)
```

# Specification 1

```{r}
# scored_browsing_tbl %>% 
#   filter(stage != 'treatment') %>%
#   group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
#   mutate(
#     scored_perday_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
#   ) %>%
#   ungroup %>% group_by(id, days_since_appearance, total_active_time_s) %>%
#   mutate(
#     total_perday_active_time_s = sum(total_active_time_s, na.rm=T) # computes total active time on scored domains for the day
#   ) %>%
#   sdf_pivot(id + days_since_appearance + domain + branch + scored_perday_active_time_s + total_perday_active_time_s ~ stage) %>%
#   mutate(
#     scaled_scored_active_time_s = scored_perday_active_time_s/total_perday_active_time_s
#   ) %>% select(-scored_perday_active_time_s, -total_perday_active_time_s) %>%
#   filter(id==1098 & domain=='aol.com')
```
```{r}
# options(scipen=10000)
# scored_browsing_tbl %>%
#   filter(stage != 'treatment') %>%
#   group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
#   mutate(
#     scored_perday_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
#   ) %>%
#   ungroup %>% group_by(id, days_since_appearance, total_active_time_s) %>%
#   mutate(
#     total_perday_active_time_s = sum(total_active_time_s, na.rm=T) # computes total active time on scored domains for the day
#   ) %>%
#   sdf_pivot(id + days_since_appearance + domain + branch + scored_perday_active_time_s + total_perday_active_time_s ~ stage) %>%
#   mutate(
#     scaled_scored_active_time_s = scored_perday_active_time_s/total_perday_active_time_s
#   ) %>% select(-scored_perday_active_time_s, -total_perday_active_time_s) %>%
#   sdf_quantile(column='scaled_scored_active_time_s', probabilities=c(0,.25,.5,.75,.9,.99,.999,1))
```

```{r}

tmp = scored_browsing_tbl %>% 
  filter(stage != 'treatment') %>%
  group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
  mutate(
    scored_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
  ) %>%
  ungroup %>% group_by(id, days_since_appearance, total_active_time_s) %>%
  mutate(
    total_perday_active_time_s = sum(total_active_time_s, na.rm=T) # computes total active time on scored domains for the day
  ) 

tmp
sdf_quantile(tmp, column='scored_active_time_s', probabilities=c(0,.25,.5,.75,.9,.99,.999,1))
sdf_quantile(tmp, column='total_perday_active_time_s', probabilities=c(0,.25,.5,.75,.9,.99,.999,1))


spec1a_tbl = scored_browsing_tbl %>% 
  filter(stage != 'treatment') %>%
  group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
  mutate(
    scored_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
  ) %>%
  ungroup %>%
  select(-mean_active_time_s, -score) %>%
  group_by(id, stage, branch) %>%
  mutate(
    avg_scored_active_time_s = mean(scored_active_time_s, na.rm=T)
  ) %>% 
  ungroup %>% select(-scored_active_time_s, -total_active_time_s, -domain) %>%
  sdf_pivot(id + branch + avg_scored_active_time_s ~ stage) %>%
  mutate(
     posttreatment = (posttreatment/posttreatment)*avg_scored_active_time_s, # fill treatment dummy with mean value
     pretreatment = (pretreatment/pretreatment)*avg_scored_active_time_s # fill treatment dummy with mean value
   ) %>% 
  ungroup %>% group_by(id, branch) %>%
  mutate(
   posttreatment = sum(posttreatment, na.rm=T),
   pretreatment = sum(pretreatment, na.rm=T)
  ) %>%
  collect %>%
  distinct(id, .keep_all=T)
```

Posttreatment - mean( post-treatment average time on site x bias of site )
Pretreatment - mean( pre-treatment average time on site x bias of site )
Branch - bias, whois, control

Unit of analysis is single user
```{r}
paste('Number of missing posttreatments =', sum(is.na(spec1a_tbl$posttreatment)))
paste('Number of missing pretreatments =', sum(is.na(spec1a_tbl$pretreatment)))
paste('Number of rows =', dim(spec1a_tbl)[1])

fit1a = glm(posttreatment ~ pretreatment*branch + branch, data=spec1a_tbl)
sjt.glm(fit1a)
plot_model(fit1a, rm.terms = 'pretreatment')
stargazer(fit1a)
```



# Specification 2

Average time on site (post) ~ Average time on site (pre) + alignment (bias) * branch + (1|site)

```{r}
spec2a_tbl = scored_browsing_tbl %>% 
  filter(stage != 'treatment') %>%
  sdf_pivot(id + days_since_appearance + domain + score + branch + mean_active_time_s ~ stage) %>%
  mutate(
    posttreatment = posttreatment*mean_active_time_s, # fill treatment dummy with mean value
    pretreatment = pretreatment*mean_active_time_s # fill treatment dummy with mean value
  ) %>%
  group_by(id, domain) %>%
  select(-mean_active_time_s) %>%
  mutate(
   posttreatment = log(sum(posttreatment, na.rm=T)),
   pretreatment = log(sum(pretreatment, na.rm=T))
  ) %>%
  na.replace(0) %>%
  #filter(row_number(id) == 1) %>% ungroup %>%
  collect

spec2b_tbl = scored_browsing_tbl %>% 
  filter(stage != 'treatment') %>%
  sdf_pivot(id + domain + score + branch + mean_active_time_s ~ stage) %>% # creates columns for stage dummy
  mutate(
    posttreatment = posttreatment*mean_active_time_s,
    pretreatment = pretreatment*mean_active_time_s
  ) %>%
  group_by(id, domain) %>%
  select(-mean_active_time_s) %>%
  mutate(
   posttreatment = log(sum(posttreatment, na.rm=T)),
   pretreatment = log(sum(pretreatment, na.rm=T))
  ) %>%
  filter(row_number(id) == 1) %>% ungroup() %>%
  na.replace(0) %>%
  collect

spec2c_tbl = scored_browsing_tbl %>%
  filter(stage != 'treatment') %>%
  group_by(id, domain, score, mean_active_time_s, days_since_appearance) %>%
  mutate(
    scored_avg_perday_active_time_s = mean_active_time_s * abs(score) # gets site * score of site
  ) %>%
  ungroup %>%
  sdf_pivot(id + days_since_appearance + domain + branch + score + scored_avg_perday_active_time_s ~ stage) %>%
  mutate(
    posttreatment = log(posttreatment*scored_avg_perday_active_time_s), # fill treatment dummy with mean value
    pretreatment = log(pretreatment*scored_avg_perday_active_time_s) # fill treatment dummy with mean value
  ) %>%
  ungroup %>% select(-scored_avg_perday_active_time_s) %>%
  group_by(id, domain, score, days_since_appearance) %>%
  arrange(id, days_since_appearance) %>%
  na.replace(0) %>%
  collect
```
```{r}
spec2a_tbl %>% filter(id==1098)
spec2b_tbl %>% filter(id==1098)
spec2c_tbl %>% filter(id==1098)
```

```{r}

spec2a_tbl$branch = factor(spec2a_tbl$branch)
fit2a = lmer(posttreatment ~ pretreatment + abs(score) * branch + (1|id), data=spec2a_tbl)
sjt.lmer(fit2a)
plot_model(fit2a, rm.terms = 'pretreatment', 'abs(score)')

spec2b_tbl$branch = factor(spec2b_tbl$branch)
fit2b = lmer(posttreatment ~ pretreatment + abs(score) * branch + (1|id), data=spec2b_tbl)
sjt.lmer(fit2b)
plot_model(fit2b, rm.terms = 'pretreatment', 'abs(score)')

spec2c_tbl$branch = factor(spec2c_tbl$branch)
fit2c = lmer(posttreatment ~ pretreatment + abs(score) * branch + (1|id), data=spec2c_tbl)
sjt.lmer(fit2c)
plot_model(fit2c, rm.terms = c('pretreatment', 'abs(score)'))

stargazer(fit2a, fit2b, fit3c)
```

# Specification 3 

Has average score changed over time?

```{r}
spec3_tbl = scored_browsing_tbl %>% 
  filter(stage=='pretreatment' | stage=='treatment' | stage=='posttreatment') %>%
  group_by(id, stage, days_since_appearance, score) %>%
  mutate(
    daily_avg_score = mean(score, na.rm=T)
  ) %>% select(-mean_active_time_s, -total_active_time_s) %>%
  collect

ggplot(spec3_tbl, aes(
       x=days_since_appearance,
       y=daily_avg_score,
       color=stage,
       group=days_since_appearance)) +
  geom_boxplot()
```
```{r}
spec3_tbl = spec3_tbl %>%
  inner_join(pid_tbl, copy=T) %>%
  filter(pid == 'D' | pid == 'R' | pid == 'SD' | pid == 'SR') %>%
  group_by(id, stage, days_since_appearance, score) %>%
  mutate(
    daily_avg_score = mean(score, na.rm=T)
  ) %>% 
  collect

ggplot(spec3_tbl, aes(
       x=days_since_appearance,
       y=daily_avg_score,
       color=stage,
       group=days_since_appearance)) +
  geom_boxplot() + facet_wrap(~pid)
```
```{r}
ggplot(spec3_tbl, aes(
       x=days_since_appearance,
       y=daily_avg_score,
       fill=branch,
       group=days_since_appearance)) +
  geom_boxplot(position='dodge') + facet_wrap(~stage)
```

