---
title: "Preliminary analysis"
output: 
  html_document:
    keep_md: true
---
We begin with a description of the population itself.

# Data cleaning and preparation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  cache.path = '/home/hadoop/analyses/rweiss/pioneer-news-analysis/cache/',
  cache.extra = list(R.version, sessionInfo(), format(Sys.Date(), '%Y-%m')),
  fig.path = "fig/")

source('/home/hadoop/analyses/rweiss/pioneer-news-analysis/make_browsing_tables.R')
source('/home/hadoop/analyses/rweiss/pioneer-news-analysis/recode_survey.R')
```


## Distribution of activity during the study period
```{r enrollment_plots}
visitdate_df = activity_tbl %>% 
  group_by(id, visit_start_date, stage) %>%
  count %>% collect

startdate_df = activity_tbl %>% 
  group_by(id, days_since_appearance, stage) %>%
  count %>% collect

ggplot(visitdate_df, aes(
  x=visit_start_date,
  y=n,
  color=stage
)) +
  geom_bar(stat='identity', width=.5) +
  guides(color=F) +
  theme_bw() + scale_color_solarized() + 
  labs(title = "Total domain dwell events observed during study by calendar date", subtitle = "Colored by enrollment period") +
  xlab('Date during study') + ylab('Total dwell events observed')

ggplot(startdate_df, aes(
  x=days_since_appearance,
  y=n,
  color=stage
)) +
  geom_bar(stat='identity', width=.5)+
  guides(color=F) +
  theme_bw() + scale_color_solarized() + 
  labs(title = "Total domain dwell events observed during study by enrollment date", subtitle = "Colored by enrollment period") +
  xlab('Days since enrollment') + ylab('Total dwell events observed')

ggplot(startdate_df, aes(
  x=days_since_appearance,
  y=log(n),
  group=days_since_appearance,
  color=stage)) +
  geom_boxplot() +
  guides(color=F) +
  theme_bw() + scale_color_solarized() +
  labs(title = "Logged total domain dwell events observed during study by enrollment date", subtitle = "Colored by enrollment period") +
  xlab('Days since enrollment') + ylab('Total dwell events observed')
```

## General activity of enrollees over all study periods
```{r daysactive_plots}
ecdf_activedays_df = activity_tbl %>%
  group_by(visit_start_date, branch, id) %>%
  count %>%
  filter(n>0)%>%
  group_by(id, branch)%>%
  count %>%
  collect

ggplot(ecdf_activedays_df, aes(nn)) + geom_histogram(binwidth=1,position='dodge') + 
  theme_bw()+
  labs(title = "Observed distribution of participant active days", subtitle = "Over all study periods")

ggplot(ecdf_activedays_df, aes(nn)) + stat_ecdf(geom='step') + 
  theme_bw() +
  labs(title = "Cumulative distribution of participant active days", subtitle = "Over all study periods")

ggplot(ecdf_activedays_df, aes(nn, fill=branch)) + 
  geom_histogram(binwidth=1,position='dodge') + 
  scale_fill_canva(palette='Tropical tones', 
                    guide=guide_legend(title='', label.position='bottom')) +
  labs(title = "Observed distribution of participant active days by branch", subtitle = "By branch") +
  theme_bw() + theme(legend.position="bottom")

ggplot(ecdf_activedays_df, aes(nn, color=branch)) + stat_ecdf(geom='step') + 
  scale_color_canva(palette='Tropical tones', 
                    guide=guide_legend(title='', label.position='bottom')) +
  theme_bw()+ theme(legend.position="bottom") +
  labs(title = "Cumulative distribution of participant active days", subtitle = "By branch")

```

### Without weekends?
```{r wdaysactive_plots}
pdf_activewdays_df = activity_tbl %>%
  group_by(visit_start_date, branch, id) %>%
  count %>%
  collect %>%
  mutate(wday=wday(visit_start_date)) %>%
  filter(n>0)%>%
  ungroup %>% group_by(wday) %>%
  count %>% collect

ecdf_activewdays_df = activity_tbl %>%
  group_by(visit_start_date, branch, id) %>%
  count %>%
  collect %>%
  mutate(wday=wday(visit_start_date)) %>%
  filter(n>0 & wday !=1 & wday !=7)%>%
  group_by(id, branch)%>%
  count %>% collect

ggplot(ecdf_activewdays_df, aes(nn)) +
  geom_histogram(binwidth=1,position='dodge') +
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(ecdf_activewdays_df, aes(nn)) +
  stat_ecdf(geom='step') +
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(ecdf_activewdays_df, aes(nn, fill=branch)) +
  geom_histogram(binwidth=1,position='dodge') +
  scale_fill_canva(palette='Tropical tones',
                    guide=guide_legend(title='', label.position='bottom')) +
  theme_bw()+ theme(legend.position="bottom") +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(ecdf_activewdays_df, aes(nn, color=branch)) +
  stat_ecdf(geom='step') +
  theme_bw()+ theme(legend.position="bottom") +
  scale_color_canva(palette='Tropical tones',
                    guide=guide_legend(title='', label.position='bottom')) +

  labs(title = "New plot title", subtitle = "A subtitle")

kable(quantile(ecdf_activewdays_df$nn, probs=c(0, .25, .5, .75, .99, .999, .9999, 1)))

ecdf_df= data.frame(Days=quantile(ecdf_activewdays_df$nn, probs=c(0, .25, .5, .75, .99, .999, .9999, 1)))

ecdf_activedays_tab=xtable(t(ecdf_df),
                           caption='caption',
                           label='tab:ecdf_activewdays')

print(ecdf_activedays_tab,file="tables.tex",append=T,table.placement = "h",
 caption.placement="bottom", hline.after=seq(from=-1,to=nrow(ecdf_activedays_tab),by=1))



```

## Distribution of time of browsing

```{r timeofday}
hours = activity_tbl %>% 
  mutate(timestamp=hour(from_unixtime(visit_start_time))) %>% 
  select(timestamp) %>% group_by(timestamp) %>% 
  count %>% collect

#activity_tbl %>% mutate(timestamp=from_unixtime(visit_start_time)) %>% select(timestamp)
#activity_tbl %>% mutate(timestamp=from_utc_time(visit_start_time)) %>% select(timestamp)

hours$timestamp = hours(hours$timestamp)

ggplot(hours, aes(x=timestamp, y=n)) + 
  geom_bar(stat='identity') + 
  scale_y_continuous(labels=comma) +
  scale_x_time(labels = date_format("%H:%M")) +
  labs(title = "Distribution of dwell event submission times", 
       subtitle = "Transformed from UTC") + 
  xlab('Timestamp') + 
  ylab('Number of submissions') +
  theme_bw() 
```


## Average number of pageviews per day
```{r avg_pv_plots, cache=TRUE}
daily_pagevisits = activity_tbl %>%
  group_by(id,visit_start_date) %>%
  count %>%
  ungroup %>% group_by(id) %>%
  summarise(
    mu=mean(n, na.rm=T)
  ) %>%
  filter(mu<800) %>% # greater than 99.999%
  collect

ggplot(daily_pagevisits, aes(x=mu)) + 
  geom_histogram(binwidth=1) + 
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(daily_pagevisits, aes(x=mu)) + 
  stat_ecdf() + 
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(daily_pagevisits, aes(x=log(mu))) + 
  geom_histogram(binwidth=.01) + 
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(daily_pagevisits, aes(x=log(mu))) + 
  stat_ecdf() + 
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

kable(quantile(daily_pagevisits$mu, probs=c(0, .25, .5, .75, .99, .999, .9999, 1)))

daily_visits_df= data.frame(Days=quantile(daily_pagevisits$mu, probs=c(0, .25, .5, .75, .99, .999, .9999, 1)))

daily_visits_tab=xtable(t(daily_visits_df),
                           caption='nth-tiles of average daily page visits',
                           label='tab:daily_visits_mu')

print(daily_visits_tab,file="tables.tex",append=T,table.placement = "h",
 caption.placement="bottom", hline.after=seq(from=-1,to=nrow(daily_visits_tab),by=1))

```

### Average total active browsing per day
```{r avg_ab_plots, cache=TRUE}
daily_active_browsing = activity_tbl %>%
  group_by(id,days_since_appearance) %>%
  summarise(total_s=sum(total_active_time, na.rm=T)) %>%
  filter(total_s<17290.93) %>%
  mutate(total_m=total_s/60) %>%
  mutate(total_h=total_m/24) %>%
  filter(total_m>1)%>%
  collect

ggplot(daily_active_browsing, aes(x=total_h)) + 
  stat_ecdf() + 
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(daily_active_browsing, aes(x=log(total_h))) + 
  stat_ecdf() + 
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(daily_active_browsing, aes(x=total_m)) + 
  stat_ecdf() + 
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(daily_active_browsing, aes(x=log(total_m))) + 
  stat_ecdf() + 
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(daily_active_browsing, aes(x=total_h)) + 
  geom_histogram(bins=1000, labels=comma) + 
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(daily_active_browsing, aes(x=total_m)) + 
  geom_histogram(bins=1000, labels=comma) + 
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

ggplot(daily_active_browsing, aes(x=log(total_m))) + 
  geom_histogram(bins=1000, labels=comma) + 
  theme_bw() +
  labs(title = "New plot title", subtitle = "A subtitle")

kable(quantile(daily_active_browsing$total_m, probs=c(0, .25, .5, .75, .99, .999, .9999, 1)))


daily_activity_df= data.frame(Days=quantile(daily_active_browsing$total_m, probs=c(0, .25, .5, .75, .99, .999, .9999, 1)))

daily_activity_tab=xtable(t(daily_activity_df),
                           caption='nth-tiles of average total daily active browsing (minutes)',
                           label='tab:daily_total_activity_minutes')

print(daily_activity_tab,file="tables.tex",append=T,table.placement = "h",
 caption.placement="bottom", hline.after=seq(from=-1,to=nrow(daily_activity_tab),by=1))


```


### Length of average site visit
```{r avg_sv_plots, cache=TRUE}
daily_avg_activity=activity_tbl %>%
   group_by(id, days_since_appearance) %>%
   summarise(
    mean=mean(total_active_time, na.rm=T),
    n = n()) %>%
  ungroup %>% group_by(days_since_appearance) %>%
  filter(mean>1) %>%
  collect

ggplot(daily_avg_activity, aes(x=mean)) + 
  geom_histogram(binwidth=.1) +
  scale_x_continuous(labels = comma) +
  scale_y_continuous(labels = comma) +
  theme_bw()

ggplot(daily_avg_activity, aes(x=log(mean))) + 
  geom_histogram(binwidth=.01) + 
  scale_y_continuous(labels = comma) +
  theme_bw()

ggplot(daily_avg_activity, aes(x=days_since_appearance, y=mean, group=days_since_appearance)) + 
  geom_boxplot() + 
  scale_y_continuous(labels = comma) +
  theme_bw()

ggplot(daily_avg_activity, aes(x=days_since_appearance, y=log(mean), group=days_since_appearance)) + 
  geom_boxplot() + 
  scale_y_continuous(labels = comma) +
  theme_bw()

kable(quantile(daily_avg_activity$mean, probs=c(0, .25, .5, .75, .99, .999, .9999, 1)))

daily_active_session_df= data.frame(Days=quantile(daily_avg_activity$mean, probs=c(0, .25, .5, .75, .99, .999, .9999, 1)))

daily_active_session_tab=xtable(t(daily_active_session_df),
                           caption='nth-tiles of average active site session length',
                           label='tab:daily_active_session')

print(daily_active_session_tab,file="tables.tex",append=T,table.placement = "h",
 caption.placement="bottom", hline.after=seq(from=-1,to=nrow(daily_active_session_tab),by=1))

```

## Self report


### Demographics: Partisan ID, Age, Gender

### Browsing patterns against self report

# Analysis

## Browsing scored domains

## Browsing scored domains by partisan group

```{r pid_browsing_visits}
#tbl_uncache(sc,'activity_tbl')

daily_pid_scored_sessions = scored_activity_tbl %>%
  inner_join(valids_tbl) %>%
  inner_join(pid_tbl) %>%
  filter(pid != 'O' & pid != 'N' & pid != 'I') %>% #| pid == 'I') %>%
  group_by(id, score, pid) %>%
  collect

ggplot(daily_pid_scored_sessions, aes(
  x=score,
  color=pid, 
  fill=pid)) + stat_density(position='dodge', geom='line', trim=T) + 
  labs(title='Density of site visits along alignment scores', 
       subtitle='By self-reported party identification',
       color='') +
  xlab('Alignment score from Bakshy, Messing, and Adamic (2015)') + ylab('Density of dwell events') +
  theme_bw() + theme(legend.position = 'bottom') +
  guides(
    color=guide_legend(label.position='bottom',title.position='top'))
```

```{r pid_browsing_sessions}
# 
# scored_activity_tbl %>% 
#   inner_join(valids_tbl) %>%
#   inner_join(pid_tbl) %>%
#   group_by(id, days_since_appearance) %>%
#   mutate(
#     daily_total_browsing_s = sum(total_active_time, na.rm=T)
#   ) %>% ungroup %>%
#   group_by(id, days_since_appearance, score) %>%
#   mutate(
#     scored_daily_total_browsing_s = sum(total_active_time, na.rm=T)
#   )
# 
#   select(-days_since_appearance) %>%
#   filter(pid != 'O' & pid != 'N' & pid != 'I' ) %>% 
#   #group_by(id, score, pid) %>%
#   #filter(id==2157) %>% 
#   group_by(id, pid, daily_total_browsing_s,score) %>%
#   summarise(
#     avg = mean(total_active_time, na.rm=T),
#     total = sum(total_active_time, na.rm=T)) %>%
#   filter(total < 6272) %>%
#   mutate(
#     scored_time = abs(score)*(total/daily_total_browsing_s)
#   ) %>%
#   collect
# 
# reps = one %>% filter(pid == 'R')
# 
# 
# ggplot(one, aes(
#   x=scored_time,
#   color=pid
# ))+ geom_density(position='dodge') +
#   scale_y_continuous(labels = comma) +
#   xlab("Scaled active time (in seconds)") +
#   ylab('Density') +
#   theme_bw() + 
#   labs(title='Density of active time on scored content',
#        subtitle='Scaled )


# daily_pid_scored_browsing = daily_pid_scored_sessions %>% 
#   group_by(pid, score, days_since_appearance) %>%
#   summarise(
#    daily_sum_time = sum(total_active_time_s, na.rm=T),
#    daily_avg_time = mean(total_active_time_s, na.rm=T)) %>%
#   collect
# ggplot(bias_scores, aes(x=avgAlign)) + stat_density(trim=T)

```


